A general and efficient representation of ancestral recombination graphs

### 2024-06-07 paper.tex
Move data availability
Add funding and Conflict of interest section
Remove supplementary figure

\section*{Acknowledgements}
We are grateful to Nick Barton, Gideon Bradburd, 
Castedo Ellerman, Alex Lewanski,
Peter Ralph and Andrew Vaughn
for helpful discussions and comments on the manuscript, and
to Iain Mathieson and Aylwyn Scally for interesting discussions that
originally motivated this work.
We are particularly grateful to Graham Coop for detailed feedback
on an earlier version of the manuscript.
% Ordered alphabetically by surname
Gregor Gorjanc acknowledges support from the BBSRC ISP grant to The Roslin Institute
(BBS/E/D/30002275, BBS/E/RL/230001A, and BBS/E/RL/230001C).
Jerome Kelleher acknowledges support from the Robertson Foundation,
NIH (research grants HG011395 and HG012473) and
EPSRC (research grant EP/X024881/1).
Jere Koskela acknowledges support from EPSRC research grant EP/V049208/1.

@@

@@

\clearpage
\renewcommand\thefigure{S\arabic{figure}}
\setcounter{figure}{0}
\renewcommand\thetable{S\arabic{table}}
\setcounter{table}{0}

\section*{Supplementary Material}

\begin{figure*}[ht]
	\begin{center}
		\includegraphics[width=0.8\textwidth]{illustrations/simplification-with-edges.pdf}
	\end{center}
	\caption{\label{fig-simplification-with-edges}
	Example ARGs Fig.~\ref{fig-simplification}A--D,
    with edges annotated with inheritance intervals.
	}
\end{figure*}

>>>>

@@

\section*{Acknowledgements}
We are grateful to Nick Barton, Gideon Bradburd, 
Castedo Ellerman, Alex Lewanski,
Peter Ralph and Andrew Vaughn
for helpful discussions and comments on the manuscript, and
to Iain Mathieson and Aylwyn Scally for interesting discussions that
originally motivated this work.
We are particularly grateful to Graham Coop for detailed feedback
on an earlier version of the manuscript.

\section*{Funding}
% Ordered alphabetically by surname
Gregor Gorjanc acknowledges support from the BBSRC ISP grant to The Roslin Institute
(BBS/E/D/30002275, BBS/E/RL/230001A, and BBS/E/RL/230001C).
Jerome Kelleher acknowledges support from the Robertson Foundation,
NIH (research grants HG011395 and HG012473) and
EPSRC (research grant EP/X024881/1).
Jere Koskela acknowledges support from EPSRC research grant EP/V049208/1.

\section*{Conflicts of Interest}
The authors declare that there is no conflict of interest.

@@

% \clearpage
% \renewcommand\thefigure{S\arabic{figure}}
% \setcounter{figure}{0}
% \renewcommand\thetable{S\arabic{table}}
% \setcounter{table}{0}

% \section*{Supplementary Material}

% \begin{figure*}[ht]
% 	\begin{center}
% 		\includegraphics[width=0.8\textwidth]{illustrations/simplification-with-edges.pdf}
% 	\end{center}
% 	\caption{\label{fig-simplification-with-edges}
% 	Example ARGs Fig.~\ref{fig-simplification}A--D,
%     with edges annotated with inheritance intervals.
% 	}
% \end{figure*}
